### 2022-11-11 NSF2022/Description/backgroundv2.tex

\subsection{Problem formulation}
Recently, we have developed a new mathematical model of
self-organization~\cite{FuQuRyYo22,fu-ryh-qua-you2022,Fu2018_SIAM}. The
model takes ideas from the phase field method and leverages boundary
integral equations to resolve complex domains and speed up computations.
To formulate the problem, consider a collection of $N_b$-many rigid
bodies $U_i(t) \subset RR^n$ with boundary $\Gamma_i(t)$. We call these
bodies ``granules''. The granules are immersed in an incompressible,
zero-Reynolds number fluid $\Omega(t) = \RR^n \setminus \cup_{i=1}^{N_b}
U_i(t)$ (Figure~\ref{fig:flow_map}).

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Boundary integral formulation}
\todo[inline]{Bryan left off here}
\label{sec:bie}
The solution of PDEs in a domain surrounding a mobile, dense suspension
of bodies is highly nontrivial and requires accurate,
dimension-reducting discretization
that do not require continual remeshing.  
Boundary integral equations (BIEs) are a reformulation of elliptic PDEs
including the Stokes equation~\eqref{eqn:stokes} and the phase
equation~\eqref{eqn:phase} in the special case of $f(u) =
\tfrac{1}{2}u^2$. Using the Stokes equation as an example, its solution
can be written as a convolution 
\begin{align*}
  \uu(\xx) = \int_{\partial\Omega(t)} G(\xx - \yy) \ssigma(\yy) \, ds_\yy,
\end{align*}
where $G(\xx - \yy)$ is a carefully chosen derivative of the PDE's
fundamental solution and $\ssigma: \partial \Omega(t) \rightarrow \RR^2$
is an unknown density function. The BIE reformulation has several
immediate advantages including a dimension reduction since $\ssigma$ is
defined only on $\partial \Omega(t)$, and the far field boundary
condition of the PDE is automatically satisfied. The density
function $\ssigma$ is chosen to satisfy the boundary condition, and this
results in a BIE 
\begin{align*}
  \gg(\xx) = \lambda \ssigma(\xx) + 
    \int_{\partial\Omega(t)} G(\xx - \yy) \ssigma(\yy) \, ds_\yy,
    \quad \xx \in \partial\Omega(t),
\end{align*}
where $\gg$ is the Dirichlet boundary condition, and $\lambda$ is a
constant that depends on the choice of $G$. For numerical stability,
choices of $G$ that result in second-kind Fredholm integral equations,
meaning $\lambda \neq 0$, are preferred.

A consequence of the dimension reduction in a BIE formulation is that
complex geometries are much easier to resolve than a mesh-based method
since only $\partial \Omega(t)$ needs to be discretized
(Figure~\ref{fig:fem_vs_bie}). Additional advantages of a BIE
formulation includes a discretization that is high-order, or even
spectrally, accurate; results in a well-conditioned linear system that
can be solved iteratively with a mesh-independent number of iterations
of a Krylov method such as the generalized minimal residual method
(GMRES). However, BIEs do have several challenges: nearly touching
granules requires a quadrature rule for nearly-singular integrals; their
discretization results in dense matrices; and they cannot immediately be
applied to non-linear PDEs. The BIE community, including PI Quaife, has
developed a variety of tools to address these numerical challenges, and
we discuss our planned approach in Section~\ref{sec:specificaim2}.

>>>>

\subsection{Problem formulation}
Recently, we have developed a new mathematical model of
self-organization~\cite{FuQuRyYo22,fu-ryh-qua-you2022,Fu2018_SIAM}. The
model takes ideas from the phase field method and leverages boundary
integral equations to resolve complex domains and speed up computations.
To formulate the problem, consider a collection of $N_b$-many rigid
bodies $U_i(t) \subset \RR^n$ with boundary $\Gamma_i(t)$. We call these
bodies ``granules''. The granules are immersed in an incompressible,
zero-Reynolds number fluid $\Omega(t) = \RR^n \setminus \cup_{i=1}^{N_b}
U_i(t)$ (Figure~\ref{fig:flow_map}).

@@

The solution of the PDEs~\eqref{eqn:stokes} and~\eqref{eqn:phse} is
challenging because of the complex and unbounded domain. Even more
troubling is when dense suspensions are considered. Integral equation
methods offer an alternative formulation of the PDEs that only require
meshing the boundary of the granules rather than all of $\Omega(t)$
(Figure~\ref{fig:fem_vs_bie}). Additional advantages of a IE formulation
includes a discretization that is high-order, or even spectrally,
accurate; results in a well-conditioned linear system that can be solved
iteratively with a mesh-independent number of iterations of a Krylov
method such as the generalized minimal residual method (GMRES). However,
IEs do have several challenges: nearly touching granules requires a
quadrature rule for nearly-singular integrals; their discretization
results in dense matrices; and they cannot immediately be applied to
non-linear PDEs. The IE community, including PI Quaife, has developed a
variety of tools to address these numerical challenges, and we discuss
our planned approach in Section~\ref{sec:specificaim2}.

@@
